Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-09-08 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:09:08	14:54:44	(Tue 8.Sep)

Assuming that a robust MVDR is the reference method we want LCA to perform similarly to, it seems sensible to create window database for LCA with responses that resembles the ones MVDR computes. We study this in \Fig{mvdr_selected_windows}, where the typical responses MVDR creates for shadow, speckle and highlight regions in the Holmengraa scene is presented.

Observe from \Fig{mvdr_selected_windows} that MVDR seems prefers symmetric window responses, even if it is free to choose non-symmetric ones. The symmetry is most predominant in shadow and speckle regions, while in highlight the windows are approximately symmetric within the illuminated\todo{valid term?} sector of the seafloor. The symmetry is a side-effect of robustifying MVDR to operate in near snapshot mode in an active system. If we look at the peak sidelobe levels of the MVDR windows they are for the most part between -13\,dB and -43\,dB. This corresponds to that of the rectangular and Hamming window, or a Kaiser window with $\beta=0$ and $\beta=2$, respectively.

We hypothesize that LCA should work even if it only selects from Kaiser windows. If they span a decent range of $\beta$-values, and some steering variations is applied to each, we should have responses that resembles those in \Fig{mvdr_selected_windows}. The Kaiser window is easy to compute, is fairly insensitive to coefficient inaccuracies, and can create windows with shapes spanning from rectangular to Gaussian.

it is optimal in the sense of having its peak power concentration near the steering angle

>>>>

Assuming that a robust MVDR is the reference method we want LCA to perform similarly to, it seems sensible to create window database for LCA with with responses similar to the ones MVDR computes. We study this in \Fig{mvdr_selected_windows}, where the typical responses MVDR creates for shadow, speckle and highlight regions in the Holmengraa scene is presented.

Observe from \Fig{mvdr_selected_windows} that MVDR seems prefers symmetric window responses, even if it is free to choose non-symmetric ones. The symmetry is most predominant in shadow and speckle regions, while in highlight the windows are approximately symmetric within the illuminated\todo{valid term?} sector of the seafloor. We have observed this symmetry to be a side-effect of running MVDR in near snapshot mode in an active system, due to the steps needed to build the sample covariance matrix.If we look at the peak sidelobe levels of the MVDR windows they are for the most part between -13\,dB and -43\,dB. This corresponds to that of the rectangular and Hamming window, or a Kaiser window with $\beta=0$ and $\beta=2$, respectively.

We hypothesize that LCA should work even if it only selects from Kaiser windows. If they span a decent range of $\beta$-values, and some steering variations is applied to each, we should have responses that resembles those in \Fig{mvdr_selected_windows}. The Kaiser window is easy to compute, is fairly insensitive to coefficient inaccuracies, and can create windows with shapes spanning from rectangular to Gaussian. It is also optimal in the sense of having its peak power concentration near the steering angle.
